|

### 2021-11-04 07-Chp-Triangulation.Rmd
Back to working version

<!-- TODO Add this to the Chapter summary in the introduction and  -->

@@

This chapter will attempt to triangulate the evidence identified by the systematic review in Chapter \ref(sys-rev-heading-results), with the the results from the analysis of CPRD data (Chapter \ref(cprd-heading) and IPD \ref(ipd-heading).

@@

@@

Qualitative triangulation is describing the different results.It has been widely used in the literature, and is comparable to Bradford-Hill's criteria of "consistency", that is the replication of an observed relationship across several different "contexts". In this framework.

@@

@@

@@

@@

In addition to the qualitative discussion of evidence, I attempted to integrate the . This approach incorporated advancements in the way that bias in results is assessed to illustrate both how causal questions could be addressed under this quantitative triangulation framework, and

@@

#### Definition of the causal questions of interest (case-studies)
<!-- TODO See ROBINS-E for this, as to how to think about exposures -->

@@

•	One interventional: Effect of average exposure to LDL-c during midlife on AD 
•	One aetiological: Effect of cumulative LDL-c from birth

As outlined in the thesis overview presented in Section \@ref(hold), the triangulation draws on the research produced in the preceding chapters.

@@

@@

## Results
### Intro

<!----------------------------------------------------------------------------->

@@

### Standardisation across study designs

@@

In this chapter, I have presented a new visualistion fo the bias inherent to each result, and suggested hwo. While this work is largely illustrative, as the correst distributions of modifying values in each risk-of-bias domain should be driven by meta-epidemiologic studies, these do not yet exist.

@@

Eliciation and bias-adjusted not as favoured versus weighting [@stone2020] <!-- TODO Check this is actually what this reference says --> though weighting at the overall risk of bias level loses some of the information contained in domain-level based assessments.

@@

### Discussion of E-values

@@

@@

@@

>>>>

<!-- TODO Add this to the Chapter summary in the introduction -->

@@

This chapter will attempt to triangulate the evidence identified by the systematic review in Chapter \@ref(sys-rev-heading-results), with the the results from the analysis of CPRD data (Chapter \@ref(cprd-heading) and IPD \@ref(ipd-heading).

@@

Aetiological triangulation, or simply triangulation, is the process of comparing and contrasting across result in order to .

It has been widely used in the literature, and is comparable to Bradford-Hill's criteria of "consistency", that is the replication of an observed relationship across several different contexts.[@hill1965] In this framework,

@@

_Qualitative_ triangulation is describing the different results. It regularly appears though not under that name, in the discussion of results section under the name "comparison with other literature".

Previous examples of this approach have used criteria such as

In contrast, _quantitative triangulation_ attempts to obtain a overall numerical result by synthesising the different types of evidence.

@@

Talk about problems of sclae - assuming bias direction at the study level works well if you only have one study per design category as in the example by Ference et al (e.g. IPD analysis of )

@@

As outlined in the thesis overview presented in Section \@ref(background-thesis-overview), the triangulation draws on the research produced in the preceding chapters.

@@

This analysis built on the detailed risk of bias assessments performed and presented as part of the systematic review (Chapter \@ref()/\@ref()), and the results of the

@@

In addition to the qualitative discussion of evidence, I attempted to integrate the numerical results of the multiple approaches.

A framework for bias-adjusted meta-analysis

The code supporting the original implementation (written as a STATA do file) was converted into R code, and

This approach incorporated advancements in the way that bias in results is assessed to illustrate both how causal questions could be addressed under this quantitative triangulation framework, and

This was implemented via a bias-adjusted meta-analytical framework.

Several steps were used to accomplish this approach, as described in the following sections.

@@

#### Definition of the causal questions of interest (case-studies)
<!-- TODO See ROBINS-E for this, as to how to think about exposures, adn the "Duration and timing of exposure being assessed with different approachesDuration and timing of exposure being assessed with different approaches" section of the aetiological triangulation -->

In the first instance, following standard triangulation

@@

*	Effect of average exposure to LDL-c during midlife on AD 
*	Effect of cumulative LDL-c from birth to mid-life on AD
* Effect of late-life LDL-c on all-cause dementia

&nbsp;

<!-- TODO This table will describe the causal questions of interest, following the ROBINS-E framework as columns, and list the included studies adn the relative weights of each. -->

<!----------------------------------------------------------------------------->
(ref:questionsOfInterest-caption) questionsOfInterest

(ref:questionsOfInterest-scaption) questionsOfInterest

```{r questionsOfInterest-table, message=FALSE, results="asis", echo = FALSE}
```
<!----------------------------------------------------------------------------->

&nbsp;

@@

####	Assign modifying values to indirectness

@@

## Results

@@

#### Intro

#### Standardisation across study designs

@@

In this chapter, I have presented a new visualisation fo the bias inherent to each result, and suggested hwo. While this work is largely illustrative, as the correst distributions of modifying values in each risk-of-bias domain should be driven by meta-epidemiological studies, these do not yet exist.

@@

Elicitation and bias-adjusted not as favoured versus weighting [@stone2020] <!-- TODO Check this is actually what this reference says --> though weighting at the overall risk of bias level loses some of the information contained in domain-level based assessments.

@@

### Alternative approaches

#### E-values

@@

As an example, I calculated the E-value required to attenuate the hamrful association observed between statin use and vascular dementia in the CPRD analysis ( `r hold()`` ) presented in Chapter \@ref(cprd-heading). Assuming an outcome prevalence of <15%, an E-value of 3.31 was identified

This calculation was performed using the XXX R package.

<!-- TODO Ensure that the example is provided first, as you then go on to disparage it - in the example given, the main driver of bias is likely to be confounding (though some may be due to misclassification) -->

However, this approach is only useful if the only source of bias in a result is due to uncontrolled confounding (as assessed by a domain-based risk of bias tool).

Otherwise, it's interpretation is more challenging, as the biasing effect is incorrectly assinged complete to confoudning, thus overestimating the expected effect of confounding.

the contribution of confounding to the bias in a result, and while it may be applicable if the only bias assessed to

@@

### Methods for combining different exposures

Present as an alternative

Well-used body of literature to combine different outcome measurements, but unclear as to how to combine

It may be possible to combine the different exposure measures

However, in my approach, I treated te

@@

This chapter has demonstrated a repurposed framework for quantitative triangulation, exploiting existing methods in evidence synthesis and developments in the assessment of different risks of bias.

It also introduce a new way to visualise the biases at work in a particular result, rather than making assumptions about the type and directions of bias at the study design level as suggested by previous work on this topic.

Finally, it highlighted the limitations of current methods for triangulation in the absence of informative priors for the impact of biases across the

### 2021-11-04 08-Discussion.Rmd
Back to working version

@@

## Implications 
### Clinical practice
### Future research

## Conclusions

### Strengths and Limitations

@@

@@

@@

P

@@

@@

Secondly, large-scale GWAS of vascular dementia should be performed, to identify associated loci that future Mendelian randomisation studies can make use of. While this is methodologically challenging, given the difficult in diagnosing "pure" vascular dementia, it would be a worthwhile endeavour, and would allow for the assessment of many genetically driven risk factors beyond those considered in this thesis.

@@

@@

Finally, substantial future work should be directed towards the conduct of meta-epidemiologocial studies to assess the impact of different bias in non-pbservational studies. While frameworks such as the one employed in Chapter \@ref(tri-heading) exist to allow for the production of bias-adjusted and triangulated estimates.

@@

>>>>

In this chapter I will summarise the principal findings from my thesis,

assess the unique contributions of this thesis to the field of research,

discuss the implications for both clinical and public health policy,

describe the overall strengths and limitations of this thesis as a whole,

suggest avenues for impactful future research based on my findings and experiences.

@@

This thesis has used multiple sources of evidence to examine the relationship between blood lipids levels and cholesterol risk.

It has highlighted the importance of including preprints in systematic review, and provided a tool to enable researchers to easily do so.

It has analysed two previously unalysed datasets, adding useful information to the evidence base

However, the thesis as a whole is subject to some strong limitations.

@@

This thesis is limited by the low response rate to data access requests, and the

The lack of large, precise studies made comparison across different types of evidence difficult, while the low number of eligible studies for a

## Implications of this research

### Clinical practice

The clinical recommendations that can be drawn from the work in this thesis are limited, due to the

however, a key limiting factor is the absence of a detailed pathological mechanism for Alzheimer's disease. Additionally, vascular dementia

However, based on the available evidence

### Public health

@@

<!-- TODO Could he get it work, could he feck. -->

@@

@@

### Inclusion of preprints

@@

Studying of factors which influence eventual publication would also help to identify the extent and strength of publication bias by providing a

Preprints also represent a key oppportunity to assess the impact of peer review on qualitivative changes within

### Evidence on vascular dementia

As discussed, there is an absence of evidence on vascular dementia across the evidence base, potentially driven y

large-scale GWAS of vascular dementia should be performed, to identify associated loci that future Mendelian randomisation studies can make use of. While this is methodologically challenging, given the difficult in diagnosing "pure" vascular dementia, it would be a worthwhile endeavour, and would allow for the assessment of many genetically driven risk factors beyond those considered in this thesis.

@@

### Reviewing of Mendelian randomisation studies

@@

Work is ongoing in this field, and new methodological work such as the release of teh MR-STROBE guidelines will aid in the future assessing by helping to improve the reporting of Mendelian randomisation studies.

Problems with reporting of MR studies will hopefully

### Empirical estimates of bias

Finally, substantial future work should be directed towards the conduct of meta-epidemiological studies to assess the impact of different bias in non-observational studies. While frameworks such as the one employed in Chapter \@ref(tri-heading) exist to allow for the production of bias-adjusted and triangulated estimates.

### Imporved analytical designs

Use of the real-world evidence approach needs to be traded off against the important limitations that t

Talk about the problems with real world evidence, and highlight that even when using these techniques, you still don't get the correct answers.

Tie in with GDS comments on off-targets effect.

@@

This thesis has made unique and novel contributions to the

Illustrating that commonly employed approaches to address

### 2021-11-04 tmp.Rmd
Updates
Back to working version

<!----------------------------------------------------------------------------->
(ref:covariateDef-caption) Definition of covariates adjusted for in the full-adjusted model. The codelists used to define the majority of these covariates were originally created for use in a previously published analysis.[@walker2020] while otherss were built on or adapted from previous published work.[@khan2010; @taylor2016; @wright2017]

>>>>

<!----------------------------------------------------------------------------->
(ref:covariateDef-caption) Definition of covariates adjusted for in the full-adjusted model. The codelists used to define the majority of these covariates were originally created for use in a previously published analysis.[@walker2020] while others were built on or adapted from previous published work.[@khan2010; @taylor2016; @wright2017]
